\documentclass{../cshonours}
\usepackage{subfiles}
\usepackage{url}
\usepackage{graphics}
\usepackage{etoolbox}
\usepackage{bibunits}
\usepackage{amsfonts}
\usepackage{fixltx2e}
\usepackage{tabularx}
\usepackage{accsupp}
\usepackage{pifont}
\usepackage{abbrevs}
\usepackage{acronym}
\usepackage[plain]{fancyref}
\usepackage{threeparttable}
\usepackage{tikz}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{ccicons}
\usepackage{textcomp}
\usepackage{multicol}
\usepackage{enumerate}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{calc}
\usepackage{color}
\usepackage[chapter]{minted}
\usepackage{pdflscape}
\usepackage{upquote}
\usepackage{afterpage}
\usepackage{verbatim}
\usepackage{float}
\usepackage{rotfloat}
\usepackage{gensymb}
\usepackage{gnuplot-lua-tikz}
\usepackage{subcaption}
\usepackage{afterpage}

% Blank page command
\newcommand\blankpage{%
    \null
    \thispagestyle{empty}%
    \addtocounter{page}{-1}%
    \newpage}

% TODO: Change title
\newcommand{\thetitle}{Towards a Low-Cost, Non-Invasive System for Occupancy Detection using a Thermal Detector Array}
\newcommand{\theauthor}{Ash Tyndall}

\newcommand{\thekeywords}{Internet of Things, Low-Cost Sensing, Non-Invasive Sensing, Occupancy Sensing, Smart Homes, Thermal Sensing}
\newcommand{\thecategories}{C.3, I.2.6, I.2.10, I.4.7, I.5.2, J.7} % TODO: Check categories

%%% BEGIN LATEX TWEAKS

% Tikz initialize
\usetikzlibrary{shapes, arrows, positioning, fit}
\tikzstyle{dashbox} = [rectangle, dashed, draw=black]
\tikzstyle{box} = [rectangle, draw=black, minimum width=3cm, minimum height=1cm, text centered, text width=3cm]
\tikzstyle{cbox} = [cloud, cloud puffs=15.7, minimum height=1cm, draw]
\tikzstyle{line} = [thin,-,>=stealth]
\tikzstyle{fbox} = [box, dotted, rounded corners=1mm]
\tikzstyle{fcont} = [rectangle, draw=black, minimum width=6cm, minimum height=2.5cm, text centered, text width=6cm]
\tikzstyle{circ} = [circle, draw=black, text centered,  minimum width=2cm, text width=2cm]

% Check marks and cross marks
\newcommand{\cmark}{\hspace{7mm}\BeginAccSupp{ActualText=Y}\checkmark\EndAccSupp{}}
\newcommand{\xmark}{\hspace{7mm}\BeginAccSupp{ActualText=N}\ding{55}\EndAccSupp{}}
\newcommand{\ssup}{\textsuperscript{1}}
\newcommand{\tsup}{\textsuperscript{2}}

% Configure bibliography
\bibliographystyle{acm}
\defaultbibliography{../references/primary}
\defaultbibliographystyle{acm}

% Namelist stuff for proposal
\newcommand{\namelistlabel}[1]{\mbox{#1}\hfil}
\newenvironment{namelist}[1]{%1
\begin{list}{}
    {
        \let\makelabel\namelistlabel
        \settowidth{\labelwidth}{#1}
        \setlength{\leftmargin}{1.1\labelwidth}
    }
  }{%1
\end{list}}

% Additional table options
\newcommand*{\csbox}[1]{\parbox[c]{1.7cm}{\centering #1}}
\newcolumntype{"}{@{\hskip\tabcolsep\vrule width 1pt\hskip\tabcolsep}}

% Acronyms for common stuff
\newcommand{\acrodefn}[3]{%
	\acrodef{#1}[#2]{#3}%
	\expandafter\newcommand\csname#1\endcsname{\ac{#1}\xspace}%
}

\acrodefn{pir}{PIR}{Passive Infrared Sensor}
\acrodefn{iar}{TDA}{Thermal Detector Array}
\acrodefn{mlx}{\textit{Melexis}}{Melexis MLX90620}
\acrodefn{emwa}{EMWA}{Exponential Weighted Moving Average}
\acrodefn{lowpan}{6LoWPAN}{IPv6 over Low power Wireless Personal Area Networks}
\acrodefn{coap}{CoAP}{Constrained Application Protocol}
\acrodefn{iot}{IoT}{Internet of Things}
\acrodefn{rest}{REST}{Representational state transfer}
\acrodefn{roll}{RPL}{IPv6 Routing Protocol for Low-Power and Lossy Networks}
\acrodefn{ws}{WS-*}{Web Services Descriptive Language / Simple Object Access Protocol}
\acrodefn{tarl}{TArL}{the Thermal Array Library}

% Abbreviation commands for common stuff
\newcommand{\cdi}{CO\textsubscript{2}\xspace}
\newcommand{\etal}{et al.\xspace}
\newcommand{\iic}{$\textrm{I}^2\textrm{C}$\xspace}
\newcommand{\geye}{Grid-EYE\xspace}
\newcommand{\ard}{Arduino\xspace}
\newcommand{\dc}{\degree\textrm{C}\xspace}

% Fancyref support for subsections, source; https://github.com/openlilylib/tutorials/blob/master/aGervasoni/orchestralScores/example-materials/OLLbase.sty
\newcommand*{\fancyrefsubseclabelprefix}{subsec}

\fancyrefaddcaptions{english}{%
  \providecommand*{\frefsubsecname}{subsection}%
  \providecommand*{\Frefsubsecname}{Subsection}%
}

\frefformat{plain}{\fancyrefsubseclabelprefix}{\frefsubsecname\fancyrefdefaultspacing#1}
\Frefformat{plain}{\fancyrefsubseclabelprefix}{\Frefsubsecname\fancyrefdefaultspacing#1}

\frefformat{vario}{\fancyrefsubseclabelprefix}{%
  \frefsubsecname\fancyrefdefaultspacing#1#3%
}
\Frefformat{vario}{\fancyrefsubseclabelprefix}{%
  \Frefsubsecname\fancyrefdefaultspacing#1#3%
}

% Fancyref support for subsubsections, source; https://github.com/openlilylib/tutorials/blob/master/aGervasoni/orchestralScores/example-materials/OLLbase.sty
\newcommand*{\fancyrefsubsubseclabelprefix}{subsubsec}

\fancyrefaddcaptions{english}{%
  \providecommand*{\frefsubsubsecname}{subsection}% the same as for subsection
  \providecommand*{\Frefsubsubsecname}{Subsection}%
}

\frefformat{plain}{\fancyrefsubsubseclabelprefix}{\frefsubsubsecname\fancyrefdefaultspacing#1}
\Frefformat{plain}{\fancyrefsubsubseclabelprefix}{\Frefsubsubsecname\fancyrefdefaultspacing#1}

\frefformat{vario}{\fancyrefsubsubseclabelprefix}{%
  \frefsubsubsecname\fancyrefdefaultspacing#1#3%
}
\Frefformat{vario}{\fancyrefsubsubseclabelprefix}{%
  \Frefsubsubsecname\fancyrefdefaultspacing#1#3%
}

% Fancyref support for listings, source; http://tex.stackexchange.com/questions/70835/how-to-extend-fancyref-for-listings
\newcommand*{\fancyreflstlabelprefix}{lst}

\fancyrefaddcaptions{english}{%
  \providecommand*{\freflstname}{listing}%
  \providecommand*{\Freflstname}{Listing}%
}

\frefformat{plain}{\fancyreflstlabelprefix}{\freflstname\fancyrefdefaultspacing#1}
\Frefformat{plain}{\fancyreflstlabelprefix}{\Freflstname\fancyrefdefaultspacing#1}

\frefformat{vario}{\fancyreflstlabelprefix}{%
  \freflstname\fancyrefdefaultspacing#1#3%
}
\Frefformat{vario}{\fancyreflstlabelprefix}{%
  \Freflstname\fancyrefdefaultspacing#1#3%
}

% Enable subsubsections
\setcounter{secnumdepth}{3} % Enable level 4-5
\setcounter{tocdepth}{3}    % Include level 4-5 in TOC

% Reset acronym definitions in each section and chapter
\preto\section\acresetall
\preto\chapter\acresetall

% Hyperref setup
\hypersetup{pdftitle=\thetitle,pdfauthor=\theauthor,pdfsubject=\thecategories,pdfkeywords=\thekeywords,hidelinks}

% Square table config
\newcolumntype{z}[1] {
  @{{\centering \parbox[c]{\tabcolsep}{\rule{0pt}{#1 + 2\tabcolsep}}}}
  >{\centering\arraybackslash}
  m{#1} }
% 
\renewcommand{\tabularxcolumn}[1]{z{#1}}

% TOC in PDF bookmarks
\makeatletter
\usepackage{etoolbox}
\pretocmd{\tableofcontents}{%
  \if@openright\cleardoublepage\else\clearpage\fi
  \pdfbookmark[0]{\contentsname}{toc}%
}{}{}%
\makeatother

\makeatletter
\usepackage{etoolbox}
\pretocmd{\listoffigures}{%
  \if@openright\cleardoublepage\else\clearpage\fi
  \pdfbookmark[0]{\listfigurename}{lof}%
}{}{}%
\makeatother

\makeatletter
\usepackage{etoolbox}
\pretocmd{\listoftables}{%
  \if@openright\cleardoublepage\else\clearpage\fi
  \pdfbookmark[0]{\listtablename}{lot}%
}{}{}%
\makeatother

% Fix list of listings with minted
\renewcommand{\listoflistings}{%
  \cleardoublepage
  %\addcontentsline{toc}{chapter}{\listoflistingscaption}%
  \listof{listing}{\listoflistingscaption}%
}

% Configure titles
\title{\thetitle}
\author{\theauthor}
\keywords{\thekeywords}
\categories{\thecategories}
%%% END LATEX TWEAKS

\begin{document}
\newcommand{\mainfile}{} % we use the existance of this command to see if we're compiling the whole thesis or just a chapter

\maketitle



\begin{abstract}
%Systems that detect occupancy, the presence of people, are able to save energy and greenhouse gas emissions in large buildings, and can help automate systems for the disabled in small smart homes.
%The goal of this project is to develop a low-cost sensing system that can detect room-level occupancy in a cheap, privacy-preserving, energy efficient and reliable way.
%To that end, we developed a sensing system that used a low-resolution thermal detector array and trained a variety of machine learning classification algorithms to determine the number of occupants present in the produced images.
%We found the sensor to have sufficient accuracy for per-room person detection, and that with new machine learning methods, our system improved upon the results of previous papers.

With the increasing inter-networked and inexpensive nature of embedded systems and systems, occupancy sensing, the detection of the presence and number of people in a given space, is becoming a cost-effective area of research. Knowing the number of occupants in a space can help reduce energy consumption and greenhouse gas emissions in both small homes and in large office buildings through more efficient climate control. The goal of this project is to develop an occupant sensing system that is low-cost, non-invasive, reliable and energy efficient.

After examining the available sensing options, we concluded that a low-resolution thermal sensor would be the most appropriate sensor for our project, as it has key non-invasive advantages. The key paper in that area, ThermoSense, used such a sensor in combination with image subtraction, feature extraction and machine learning algorithms to make occupancy predictions with a Root Mean Squared Error (RMSE) of only 0.35 occupants. However, due to component availability issues, ThermoSense could not be directly replicated in the Australian market.

We designed our own sensing system for \$170 based on ThermoSense using an Arduino, a Raspberry Pi, and the MLX90620 sensor, which differed from ThemoSense's in having a narrower, rectangular field of view. On top of the hardware prototype, we developed \tarl, a software library that reimplemented ThermoSense's occupant detection algorithm. We attempted to replicate the ThermoSense classification results, which used numeric Multi-Layer Perceptron, $k$-Nearest Neighbors and Linear Regression classification models, however our results were consistently poorer in both RMSE and correlation coefficient. After further experimentation with our own suite of nominal classification algorithms we were able to improve upon Thermosense's results, with the K* classification algorithm achieving a lower RMSE of 0.304 occupants. We also determine that the sensing system consumes 51mA of power when active.

We reflect upon our four criteria, and with our choice of sensor, falling component costs, our accuracy results and power consumption statistics, we conclude that our sensing system prototype meets these criteria.
\end{abstract}

\newpage
\null
\vfill 
\noindent{\fontsize{40pt}{1em}\selectfont \ccbysa}

\null

\noindent\textcopyright\xspace 2014--15 Ashley Ben Tyndall, \url{http://ash.id.au/}

\noindent This document is released under the Creative Commons Attribution-ShareAlike 4.0 International License. A copy of this license can be found at \\ \url{http://creativecommons.org/licenses/by-sa/4.0/}.

\noindent The \LaTeX{} source of this document and supporting files, such as raw data and diagrams, can be found at \url{http://ash.id.au/honours}. % TODO: Change URLS to ash.id.au redirs

\noindent The following text can be used to satisfy attribution requirements:

\noindent ``This work is based on the honours research project of Ash Tyndall, developed with the help of the School of Computer Science and Software Engineering at The University of Western Australia. A copy of this project can be found at \\ \url{http://ash.id.au/honours}.''
	
\noindent Code and code excerpts included in this document are instead released under the GNU General Public License v3 (\url{http://gnu.org/copyleft/gpl.html}), and can be found in their entirety at the same URL.

\newpage

\begin{acknowledgements}
Writing this dissertation has been my first substantial foray into academic research, and I could not have done it without the assistance and support of so many people.

Firstly, my supervisors Professor Rachel Cardell-Oliver and Professor Adrian Keating have been fundamental to this project's success. Rachel's ability to steer me away from completely redefining the project's parameters at every setback has been of critical importance, as has been her encouragement and computer science advice. Similarly, without Adrian's enviable knowledge of electronics, his skill in constructing prototypes, and his valuable perspective on thermal sensing, this project could not have happened.

Secondly, I wish to acknowledge the generous support of the University, the University Alumni, and the Hackett Foundation through the Hackett Foundation Alumni Honours Scholarship, which I was awarded at the beginning of my project. The financial support this scholarship provided has allowed me to commit more of my time to my research over working, and I can safely say that without it, my research would be of a much poorer quality.

Thirdly, to my friends and family, who have provided support and encouragement throughout this project, thank you. I cannot imagine where I would be right now without them. % TODO: Mention specific names

Additionally, I would like to acknowledge Alex Beltran, Varick L. Erickson and Alberto E. Cerpa, the authors of ThermoSense \cite{beltran2013thermosense}. Without their groundwork on thermal occupancy sensing, nothing in this dissertation would be possible.

Finally, I would like to acknowledge Linda Salzman Sagan, ``Tompw'' and ``Holek'', the authors of \url{http://commons.wikimedia.org/wiki/File:Human_outline.svg}, which I have adapted for \Fref{fig:exps:3setup}.

% TODO: Acknowledge use of person outline in figures
\end{acknowledgements}

\tableofcontents
\listoftables
\listoffigures
\listoflistings


\subfile{../introduction/introduction.tex}
\subfile{../litreview/litreview.tex}
\subfile{../design/design.tex}
\subfile{../evaluation/evaluation.tex}
\subfile{../conclusion/conclusion.tex}

\addcontentsline{toc}{chapter}{Bibliography}
\bibliography{../references/primary}

%TC:ignore
\appendix
\include{appendices}
%TC:endignore

%\clearpage



\end{document}


